Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-01 paper.tex
finish reading section 2

A basis for \(\spl_2\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
% Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.

>>>>

A basis for \(\spl_2\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{h}\) and a homomorphism \(\phi : \spl_2 \to \mathfrak{h}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
If \(\mathfrak{h}\) is semisimple, then given any nilpotent \(e \in \mathfrak{h}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{h}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{h}\), whenever \(\mathfrak{h}\) is semisimple.
In particular, we can find a Slodowy slice at any nilpotent \(e \in \gl_n\), since \(\spl_n \subseteq \gl_n\) is semisimple and contains every nilpotent element of \(\gl_n\).
